Paper_analyses

### 2021-11-25 Paper_Analyses_subj_obje_arousal.Rmd
First take on MFA
initialised MFA analysis and so far things match the inferential PCAs, but we need a principle way to decide on data structure

db_forBADA1<- data.table::dcast(setDT(db_full6new_hr_fix_stim_select2_NT_no_outl_5), 
                    ssid + TAS+AQ+Group ~ stimIAPS2, value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log1p_BIO_CDA.PhasicMax', 'arousal', 'valence'))

@@

# clustering_new$=
# clustering
clustering_new_pre_PCA<- select(clustering, c(ssid, TAS, AQ, stimIAPS2,
                                              stimDescription, 
                                                  pup_basCor,Bio_Mean_HR_dif,
                                                  log_BIO_CDA.PhasicMax, arousal,
                                                  valence, fix_count, mean_fix_dur))

@@

>>>>

View(db_full6new_hr_fix_stim_select2_NT_no_outl_5)
db_forBADA1<- data.table::dcast(setDT(db_full6new_hr_fix_stim_select2_NT_no_outl_5), 
                    ssid + TAS+AQ+Group ~ stimIAPS2, value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log1p_BIO_CDA.PhasicMax', 'arousal', 'valence'))

@@

# clustering_new$=
# clustering
View(clustering)
clustering_new_pre_PCA<- select(clustering, c(ssid, TAS, AQ, stimIAPS2,
                                              stimDescription, 
                                                  pup_basCor,Bio_Mean_HR_dif,
                                                  log_BIO_CDA.PhasicMax, arousal,
                                                  valence, fix_count, mean_fix_dur))
View(clustering_new_pre_PCA)

@@

View(all.data3_forPCA_withar)

View(clustering_new_pre_PCA)
```

Multiple factor analysys

- consider aggregating  (average per stim)
- PCA on arousal arousal and valence

library(factoextra)
library(FactoMineR)

clustering_new_pre_PCA
colnames(clustering_new_pre_PCA)

clustering_new_pre_PCA_2<- clustering_new_pre_PCA[, c(1,5:10,12)]
colnames(clustering_new_pre_PCA_2)

MFA(base, group, type = rep("s",length(group)), ind.sup = NULL, 
    name.group = NULL, num.group.sup = NULL, graph = TRUE)

res.mfa <- MFA(wine, 
               group = c(2, 5, 3, 10, 9, 2), 
               type = c("n", "s", "s", "s", "s", "s"),
               name.group = c("origin","odor","visual",
                              "odor.after.shaking", "taste","overall"),
               num.group.sup = c(1, 6),
               graph = FALSE)

clustering_new_pre_PCA_2

View(clustering_new_pre_PCA_2)

clustering_new_pre_PCA_2$ssid<- as.factor(clustering_new_pre_PCA_2$ssid)
?MFA

clustering_new_pre_PCA_2$stimDescription
res.mfa <- MFA(clustering_new_pre_PCA_2, 
               group = c(2, 1, 1, 1, 2, 1), 
               type = c("n", "s", "s", "s", "s", "s"),
               name.group = c("pp_stim","pupil","HR","SCR", "ar_val","fix"),
               num.group.sup = c(1,2),
               graph = TRUE)

print(res.mfa)

clustering_new_pre_PCA_2print(res.mfa)

```
```{r}
library("factoextra")
eig.val <- get_eigenvalue(res.mfa)
head(eig.val)

install.packages("MExPosition")
# ExPosition::FA

TExPosition::
# InPosition::
# TExPosition::

the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
```{r}
fviz_screeplot(res.mfa)

The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables. This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the

group <- get_mfa_var(res.mfa, "group")
group

The different components can be accessed as follow:
```{r}
# Coordinates of groups
head(group$coord)
# Cos2: quality of representation on the factore map
head(group$cos2)
# Contributions to the  dimensions
head(group$contrib)

To plot the groups of variables, type this:

```{r}
fviz_mfa_var(res.mfa, "group")

red color = active groups of variables
green color = supplementary groups of variables
The plot above illustrates the correlation between groups and dimensions. The coordinates of the four active groups on the first dimension are almost identical. This means that they contribute similarly to the first dimension. Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.

To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
```{r}
# Contribution to the first dimension
fviz_contrib(res.mfa, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa, "group", axes = 2)

```
Quantitative variables
The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables. This function returns a list containing the coordinates, the cos2 and the contribution of variables:
```{r}
quanti.var <- get_mfa_var(res.mfa, "quanti.var")
quanti.var

```
```{r}
# Coordinates
head(quanti.var$coord)
# Cos2: quality on the factore map
head(quanti.var$cos2)
# Contributions to the dimensions
head(quanti.var$contrib)

```
Correlation between quantitative variables and dimensions. The R code below plots quantitative variables colored by groups. The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette). Supplementary quantitative variables are in dashed arrow and violet color. We use repel = TRUE, to avoid text overlapping.

```{r}
fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”). We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
```{r}
fviz_mfa_var(res.mfa, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"), legend = "bottom")

```{r}
fviz_contrib(res.mfa, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")

```
Graph of individuals

```{r}
# To get the results for individuals, type this:

ind <- get_mfa_ind(res.mfa)
ind

```
To plot individuals, use the function fviz_mfa_ind() [in factoextra]. By default, individuals are colored in blue. However, like variables, it’s also possible to color individuals by their cos2 values:

```{r}
fviz_mfa_ind(res.mfa, col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = FALSE)

fviz_mfa_ind(res.mfa, 
             habillage = "Label", # color by groups 
             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

```
```{r}

clustering_new_pre_PCA_2

fviz_mfa_ind(res.mfa, 
             habillage = "stimDescription", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

fviz_mfa_ind(res.mfa, 
             habillage = "ssid", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

Aggregate one average per stim

library(factoextra)
library(FactoMineR)

colnames(clustering_agg_JASPtest)

clustering_agg_JASP_PCA_2<- clustering_agg_JASPtest [, c(1,27, 2:4)]
colnames(clustering_agg_JASP_PCA_2)

clustering_agg_JASP_PCA_2$stimIAPS2<- as.factor(clustering_agg_JASP_PCA_2$stimIAPS2)

clustering_agg_JASP_PCA_2$stimDescription<- as.factor(clustering_agg_JASP_PCA_2$stimDescription)

res.mfa_agg <- MFA(wine, 
               group = c(2, 5, 3, 10, 9, 2), 
               type = c("n", "s", "s", "s", "s", "s"),
               name.group = c("origin","odor","visual",
                              "odor.after.shaking", "taste","overall"),
               num.group.sup = c(1, 6),
               graph = FALSE)

colnames(clustering_agg_JASP_PCA_2)
res.mfa_agg <- MFA(clustering_agg_JASP_PCA_2, 
               group = c(2, 1, 1, 1), 
               type = c("n", "s", "s", "s"),
               name.group = c("stim_desc","HR","pupil","SCR"),
               num.group.sup = c(1,2),
               graph = TRUE)

print(res.mfa_agg)

```
```{r}
library("factoextra")
eig.val_agg <- get_eigenvalue(res.mfa_agg)
head(eig.val_agg)

the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
```{r}
fviz_screeplot(res.mfa_agg)

The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables. This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the

group_agg <- get_mfa_var(res.mfa_agg, "group")
group_agg

The different components can be accessed as follow:
```{r}
# Coordinates of groups
head(group_agg$coord)
# Cos2: quality of representation on the factore map
head(group_agg$cos2)
# Contributions to the  dimensions
head(group_agg$contrib)

To plot the groups of variables, type this:

```{r}
fviz_mfa_var(res.mfa_agg, "group")

red color = active groups of variables
green color = supplementary groups of variables
The plot above illustrates the correlation between groups and dimensions. The coordinates of the four active groups on the first dimension are almost identical. This means that they contribute similarly to the first dimension. Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.

To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
```{r}
# Contribution to the first dimension
fviz_contrib(res.mfa_agg, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa_agg, "group", axes = 2)

```
Quantitative variables
The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables. This function returns a list containing the coordinates, the cos2 and the contribution of variables:
```{r}
quanti.var_agg <- get_mfa_var(res.mfa_agg, "quanti.var")
quanti.var_agg

```{r}
# Coordinates
head(quanti.var_agg$coord)
# Cos2: quality on the factore map
head(quanti.var_agg$cos2)
# Contributions to the dimensions
head(quanti.var_agg$contrib)

```
Correlation between quantitative variables and dimensions. The R code below plots quantitative variables colored by groups. The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette). Supplementary quantitative variables are in dashed arrow and violet color. We use repel = TRUE, to avoid text overlapping.

```{r}
fviz_mfa_var(res.mfa_agg, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”). We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
```{r}
fviz_mfa_var(res.mfa_agg, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"), legend = "bottom")

```{r}
fviz_contrib(res.mfa_agg, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")
fviz_contrib(res.mfa_agg, choice = "quanti.var", axes = 2, top = 20,
             palette = "jco")

```
Graph of individuals

```{r}
# To get the results for individuals, type this:

ind_agg <- get_mfa_ind(res.mfa_agg)
ind_agg

```
To plot individuals, use the function fviz_mfa_ind() [in factoextra]. By default, individuals are colored in blue. However, like variables, it’s also possible to color individuals by their cos2 values:

```{r}
fviz_mfa_ind(res.mfa_agg, col.ind = "cos2", 
             # gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)
clust2_dataset$stimDescription
pp_stim
fviz_mfa_ind(res.mfa_agg, 
             habillage = "stimDescription", # color by groups 
             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

clustering_new_pre_PCA_2

fviz_mfa_ind(res.mfa_agg, 
             habillage = "stimIAPS2", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

Graph of partial individuals
The results for individuals obtained from the analysis performed with a single group are named partial individuals. In other words, an individual considered from the point of view of a single group is called partial individual.

In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual. That is, the individual viewed by all groups of variables.

For a given individual, there are as many partial points as groups of variables.

The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:

```{r}
fviz_mfa_ind(res.mfa_agg, partial = "all") 
# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:

fviz_mfa_ind(res.mfa, partial = c("1DAM", "1VAU", "2ING"))

Graph of partial axes
The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).

```{r}
fviz_mfa_axes(res.mfa_agg)

```{r}
data(wine)
View(wine)

View(clustering_new_pre_PCA_2)

colnames

```{r}
db_forPCA
colnames(db_forPCA)
library(tidyverse)
data3_forPCA_withar
all.data3_forPCA_withar$TAS_split<- if_else(all.data3_forPCA_withar$TAS > 
                                          median(all.data3_forPCA_withar$TAS, na.rm = TRUE), "High", "Low")
colnames(all.data3_forPCA_withar)
db_forPCA_MFA<- all.data3_forPCA_withar[, c(1,228, 4:171)]

colnames(db_forPCA_MFA)

db_forPCA_MFA

db_forPCA_MFA$ssid<- as.factor(db_forPCA_MFA$ssid)

colnames(db_forPCA_MFA)

db_forPCA_MFA$arousal_9561SickKitty<- NULL
res.mfa_dcast <- MFA(db_forPCA_MFA, 
               group = c(2, 56, 56, 56), 
               type = c("n", "s", "s", "s"),
               name.group = c("pp_gr","pupil","HR","SCR"),
               num.group.sup = c(1,2),
               graph = TRUE)

print(res.mfa_dcast)

here

```{r}
library("factoextra")
# res.mfa_dcast <- get_eigenvalue(res.mfa_dcast)
# head(res.mfa_dcast)

the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
```{r}
fviz_screeplot(res.mfa_dcast)

The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables. This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the

group_dcast <- get_mfa_var(res.mfa_dcast, "group")
group_dcast

The different components can be accessed as follow:
```{r}
# Coordinates of groups
head(group_dcast$coord)
# Cos2: quality of representation on the factore map
head(group_dcast$cos2)
# Contributions to the  dimensions
head(group_dcast$contrib)

To plot the groups of variables, type this:

```{r}
fviz_mfa_var(res.mfa_dcast, "group")

red color = active groups of variables
green color = supplementary groups of variables
The plot above illustrates the correlation between groups and dimensions. The coordinates of the four active groups on the first dimension are almost identical. This means that they contribute similarly to the first dimension. Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.

To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
```{r}
# Contribution to the first dimension
fviz_contrib(res.mfa_dcast, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa_dcast, "group", axes = 2)

```
Quantitative variables
The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables. This function returns a list containing the coordinates, the cos2 and the contribution of variables:
```{r}
quanti.var_dcast <- get_mfa_var(res.mfa_dcast, "quanti.var")
quanti.var_dcast

```{r}
# Coordinates
head(quanti.var_dcast$coord)
# Cos2: quality on the factore map
head(quanti.var_dcast$cos2)
# Contributions to the dimensions
head(quanti.var_dcast$contrib)

```
Correlation between quantitative variables and dimensions. The R code below plots quantitative variables colored by groups. The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette). Supplementary quantitative variables are in dashed arrow and violet color. We use repel = TRUE, to avoid text overlapping.

```{r}
fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”). We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
```{r}
fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"), legend = "bottom")

```{r}
fviz_contrib(res.mfa_dcast, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")
fviz_contrib(res.mfa_agg, choice = "quanti.var", axes = 2, top = 20,
             palette = "jco")

```
Graph of individuals

```{r}
# To get the results for individuals, type this:

ind_dcast <- get_mfa_ind(res.mfa_dcast)
ind_dcast

```
To plot individuals, use the function fviz_mfa_ind() [in factoextra]. By default, individuals are colored in blue. However, like variables, it’s also possible to color individuals by their cos2 values:

```{r}
fviz_mfa_ind(res.mfa_dcast, col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)
clust2_dataset$stimDescription
pp_stim
fviz_mfa_ind(res.mfa_dcast, 
             habillage = "TAS_split", # color by groups 
             palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

clustering_new_pre_PCA_2

fviz_mfa_ind(res.mfa_dcast, 
             habillage = "stimIAPS2", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

Graph of partial individuals
The results for individuals obtained from the analysis performed with a single group are named partial individuals. In other words, an individual considered from the point of view of a single group is called partial individual.

In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual. That is, the individual viewed by all groups of variables.

For a given individual, there are as many partial points as groups of variables.

The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:

```{r}
fviz_mfa_ind(res.mfa_dcast, partial = "all") 
# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:

Graph of partial axes
The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).

```{r}
fviz_mfa_axes(res.mfa_dcast)

<!-- neg, neutra positive -->

```{r}
data(wine)
View(wine)

View(clustering_new_pre_PCA_2)
?cut
clustering_new_pre_PCA_2$valence_split<- cut(clustering_new_pre_PCA_2$valence, 3,
                                             labels = c("neg", "mid", "positive"))

clustering_new_pre_PCA_2_agg_by_val<- clustering_new_pre_PCA_2%>%
  group_by(ssid,valence_split)%>%
  summarise_if(is.numeric, mean, na.rm = TRUE)

View(clustering_new_pre_PCA_2_agg_by_val)

colnames(clustering_new_pre_PCA_2_agg_by_val)
clustering_new_pre_PCA_2_agg_by_val_sel<- clustering_new_pre_PCA_2_agg_by_val[, c(1:7)]

# dcast
library(data.table)
clustering_new_pre_PCA_2_agg_by_val_sel_dcast<- data.table::dcast(setDT(clustering_new_pre_PCA_2_agg_by_val_sel), 
                    ssid ~ valence_split, value.var = c('pup_basCor',
                'Bio_Mean_HR_dif', 'log_BIO_CDA.PhasicMax', "arousal", "valence"))

clustering_new_pre_PCA_2_agg_by_val_sel_dcast

clustering_new_pre_PCA_2_agg_by_val_sel_dcast$pup_basCor_NA<- NULL

clustering_new_pre_PCA_2_agg_by_val_sel_dcast$Bio_Mean_HR_dif_NA<- NULL
clustering_new_pre_PCA_2_agg_by_val_sel_dcast$log_BIO_CDA.PhasicMax_NA<- NULL

clustering_new_pre_PCA_2_agg_by_val_sel_dcast$valence_NA<- NULL
clustering_new_pre_PCA_2_agg_by_val_sel_dcast$arousal_NA<- NULL
clustering_new_pre_PCA_2_agg_by_val_sel_dcast
View(clustering_new_pre_PCA_2_agg_by_val_sel_dcast)

namesrepl<- colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast)

namesrepl<- c("ssid", "p_neg", "p_mid" ,"p_pos", "HR_neg" , "HR_mid",
                  "HR_pos","SCR_neg", "SCR_mid", "SCR_pos")

clustering_new_pre_PCA_2_agg_by_val_sel_dcast2<- clustering_new_pre_PCA_2_agg_by_val_sel_dcast
names(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)<- namesrepl

MFA agg by val

```{r}
colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
res.mfa_agg_byval <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
               group = c(1, 3, 3, 3), 
               type = c("n", "s", "s", "s"),
               name.group = c("ssid","pupil","HR","SCR"),
               num.group.sup = c(1),
               graph = TRUE)

print(res.mfa_agg_byval)

```{r}
library("factoextra")
eif_vyval <- get_eigenvalue(res.mfa_agg_byval)
head(eif_vyval)

the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
```{r}
fviz_screeplot(res.mfa_agg_byval)

The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables. This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the

group_vybal <- get_mfa_var(res.mfa_agg_byval, "group")
group_vybal

The different components can be accessed as follow:
```{r}
# Coordinates of groups
head(group_vybal$coord)
# Cos2: quality of representation on the factore map
head(group_vybal$cos2)
# Contributions to the  dimensions
head(group_vybal$contrib)

To plot the groups of variables, type this:

```{r}
fviz_mfa_var(res.mfa_agg_byval, "group")

red color = active groups of variables
green color = supplementary groups of variables
The plot above illustrates the correlation between groups and dimensions. The coordinates of the four active groups on the first dimension are almost identical. This means that they contribute similarly to the first dimension. Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.

To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
```{r}
# Contribution to the first dimension
fviz_contrib(res.mfa_agg_byval, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa_agg_byval, "group", axes = 2)

```
Quantitative variables
The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables. This function returns a list containing the coordinates, the cos2 and the contribution of variables:
```{r}
quanti.var_agg_by_val <- get_mfa_var(res.mfa_agg_byval, "quanti.var")
quanti.var_agg_by_val

```{r}
# Coordinates
head(quanti.var_agg_by_val$coord)
# Cos2: quality on the factore map
head(quanti.var_agg_by_val$cos2)
# Contributions to the dimensions
head(quanti.var_agg_by_val$contrib)

```
Correlation between quantitative variables and dimensions. The R code below plots quantitative variables colored by groups. The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette). Supplementary quantitative variables are in dashed arrow and violet color. We use repel = TRUE, to avoid text overlapping.

```{r}
fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

Correlation between quantitative variables and dimensions. The R code below plots quantitative variables colored by groups. The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette). Supplementary quantitative variables are in dashed arrow and violet color. We use repel = TRUE, to avoid text overlapping.

```{r}
fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”). We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
```{r}
fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"), legend = "bottom")

```{r}
fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")
fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 2, top = 20,
             palette = "jco")

```
Graph of individuals

```{r}
# To get the results for individuals, type this:

ind_agg_byval <- get_mfa_ind(res.mfa_agg_byval)
ind_agg_byval

```
To plot individuals, use the function fviz_mfa_ind() [in factoextra]. By default, individuals are colored in blue. However, like variables, it’s also possible to color individuals by their cos2 values:

```{r}
fviz_mfa_ind(res.mfa_agg_byval, col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)

fviz_mfa_ind(res.mfa_agg_byval, 
             habillage = "ssid", # color by groups
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

clustering_new_pre_PCA_2

fviz_mfa_ind(res.mfa_agg_byval, 
             # habillage = "stimIAPS2", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

Graph of partial individuals
The results for individuals obtained from the analysis performed with a single group are named partial individuals. In other words, an individual considered from the point of view of a single group is called partial individual.

In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual. That is, the individual viewed by all groups of variables.

For a given individual, there are as many partial points as groups of variables.

The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:

```{r}
fviz_mfa_ind(res.mfa_agg_byval, partial = "all") 
# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:

Graph of partial axes
The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).

```{r}
fviz_mfa_axes(res.mfa_agg_byval)

with valence
clustering_new_pre_PCA_2_agg_by_val_sel_dcast

```{r}
colnames(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2)
res.mfa_agg_byval <- MFA(clustering_new_pre_PCA_2_agg_by_val_sel_dcast2, 
               group = c(1, 3, 3, 3), 
               type = c("n", "s", "s", "s"),
               name.group = c("ssid","pupil","HR","SCR"),
               num.group.sup = c(1),
               graph = TRUE)

print(res.mfa_agg_byval)

```{r}
library("factoextra")
eif_vyval <- get_eigenvalue(res.mfa_agg_byval)
head(eif_vyval)

the function fviz_eig() or fviz_screeplot() [factoextra package] can be used to draw the scree plot:
```{r}
fviz_screeplot(res.mfa_agg_byval)

The function get_mfa_var() [in factoextra] is used to extract the results for groups of variables. This function returns a list containing the coordinates, the cos2 and the contribution of groups, as well as, the

group_vybal <- get_mfa_var(res.mfa_agg_byval, "group")
group_vybal

The different components can be accessed as follow:
```{r}
# Coordinates of groups
head(group_vybal$coord)
# Cos2: quality of representation on the factore map
head(group_vybal$cos2)
# Contributions to the  dimensions
head(group_vybal$contrib)

To plot the groups of variables, type this:

```{r}
fviz_mfa_var(res.mfa_agg_byval, "group")

red color = active groups of variables
green color = supplementary groups of variables
The plot above illustrates the correlation between groups and dimensions. The coordinates of the four active groups on the first dimension are almost identical. This means that they contribute similarly to the first dimension. Concerning the second dimension, the two groups - odor and odor.after.shake - have the highest coordinates indicating a highest contribution to the second dimension.

To draw a bar plot of groups contribution to the dimensions, use the function fviz_contrib():
```{r}
# Contribution to the first dimension
fviz_contrib(res.mfa_agg_byval, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res.mfa_agg_byval, "group", axes = 2)

```
Quantitative variables
The function get_mfa_var() [in factoextra] is used to extract the results for quantitative variables. This function returns a list containing the coordinates, the cos2 and the contribution of variables:
```{r}
quanti.var_agg_by_val <- get_mfa_var(res.mfa_agg_byval, "quanti.var")
quanti.var_agg_by_val

```{r}
# Coordinates
head(quanti.var_agg_by_val$coord)
# Cos2: quality on the factore map
head(quanti.var_agg_by_val$cos2)
# Contributions to the dimensions
head(quanti.var_agg_by_val$contrib)

```
Correlation between quantitative variables and dimensions. The R code below plots quantitative variables colored by groups. The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette). Supplementary quantitative variables are in dashed arrow and violet color. We use repel = TRUE, to avoid text overlapping.

```{r}
fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

Correlation between quantitative variables and dimensions. The R code below plots quantitative variables colored by groups. The argument palette is used to change group colors (see ?ggpubr::ggpar for more information about palette). Supplementary quantitative variables are in dashed arrow and violet color. We use repel = TRUE, to avoid text overlapping.

```{r}
fviz_mfa_var(res.mfa_dcast, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

To make the plot more readable, we can use geom = c(“point”, “text”) instead of geom = c(“arrow”, “text”). We’ll change also the legend position from “right” to “bottom”, using the argument legend = “bottom”:
```{r}
fviz_mfa_var(res.mfa_agg_byval, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE,
             geom = c("point", "text"), legend = "bottom")

```{r}
fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 1, top = 20,
             palette = "jco")
fviz_contrib(res.mfa_agg_byval, choice = "quanti.var", axes = 2, top = 20,
             palette = "jco")

```
Graph of individuals

```{r}
# To get the results for individuals, type this:

ind_agg_byval <- get_mfa_ind(res.mfa_agg_byval)
ind_agg_byval

```
To plot individuals, use the function fviz_mfa_ind() [in factoextra]. By default, individuals are colored in blue. However, like variables, it’s also possible to color individuals by their cos2 values:

```{r}
fviz_mfa_ind(res.mfa_agg_byval, col.ind = "cos2", 
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)

fviz_mfa_ind(res.mfa_agg_byval, 
             habillage = "ssid", # color by groups
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

clustering_new_pre_PCA_2

fviz_mfa_ind(res.mfa_agg_byval, 
             # habillage = "stimIAPS2", # color by groups 
             # palette = c("#00AFBB", "#E7B800", "#FC4E07"),
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE # Avoid text overlapping
             )

Graph of partial individuals
The results for individuals obtained from the analysis performed with a single group are named partial individuals. In other words, an individual considered from the point of view of a single group is called partial individual.

In the default fviz_mfa_ind() plot, for a given individual, the point corresponds to the mean individual or the center of gravity of the partial points of the individual. That is, the individual viewed by all groups of variables.

For a given individual, there are as many partial points as groups of variables.

The graph of partial individuals represents each wine viewed by each group and its barycenter. To plot the partial points of all individuals, type this:

```{r}
fviz_mfa_ind(res.mfa_agg_byval, partial = "all") 
# If you want to visualize partial points for wines of interest, let say c(“1DAM”, “1VAU”, “2ING”), use this:

Graph of partial axes
The graph of partial axes shows the relationship between the principal axes of the MFA and the ones obtained from analyzing each group using either a PCA (for groups of continuous variables) or a MCA (for qualitative variables).

```{r}
fviz_mfa_axes(res.mfa_agg_byval)
